### 2020-05-29 2_task_bench.tex
Fiddle with text.

In addition to specifying the shape of the task graph, the
core API also provides implementations of the kernels
executed by each task as well as other utility routines (to parse
inputs and display results). A sample of the core API compute kernel
is shown in Listing~\ref{lst:compute-kernel}. In addition to reducing
the effort required to implement Task Bench, providing central
implementations of these services ensures that all Task Bench
implementations can be scripted uniformly and eliminates a potential
source of performance disparity that can be a pitfall for mini-apps.

>>>>

In addition to specifying the shape of the task graph, the
core API also provides implementations of the kernels
executed by each task as well as other utility routines (to parse
inputs and display results). A sample of the core API compute kernel
is shown in Listing~\ref{lst:compute-kernel}. In addition to reducing
the effort required to implement Task Bench, providing central
implementations of these services ensures that all Task Bench
implementations can be scripted uniformly and eliminates a potential
source of performance disparity that can be a pitfall for other benchmarks.
